\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter
%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Jeffrey Jing}
\newcommand{\yourEmail}{jjingdn@gmail.com}
\newcommand{\yourPhone}{626-241-8731}
\newcommand{\githubUserName}{JeffreyJing}
\newcommand{\linkedInUserName}{jeffrey-jing97}

% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsite}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsite}{abdullaharif.tech}
%     \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape \yourName} \\ \vspace{1pt}
    \small \yourPhone $|$ \href{mailto:\yourEmail}{\underline{\yourEmail}} $|$ 
    \href{https://linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}}
\end{center}


%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
\resumeHeading{Ethfinity Studios}{Founder; Blockchain, Software, \& DevOps Engineer}{Seattle, WA}{'21 - Current}
\begin{tightemize}
    \item Founded Ethfinity Studios, a blockchain product company that specializes in launching NFTs and working with Ethereum Layer2 protocols like ImmutableX.
    \item Implemented ERC721, 721A, \& 1155 smart contracts in Solidity. Built \& hosted websites to facilitate sales for clients using AWS tools including Amplify, EC2, S3 Buckets.  
    \item Projects launched: Metapengus, Deck of Degeneracy, Bobblebats, Metarelics, Relic Punks, One-Dimensional, Sneaks of Nature. All products are built on the Ethereum blockchain, with client sales totaling \$2 million.
\end{tightemize}
\sectionsep
\resumeHeading{Pathware}{Software Development Engineer}{Seattle, WA}{2020}
\begin{tightemize}
    \item Designed and implemented a Doxygen parser using \textbf{Python} web scraping that handles, processes, and re-formats information for all applicable source code files.
    %  \item Here is another bullet that I might choose to uncomment for some jobs
    \item Created an image parser that breaks down images into smaller grids for FPM technologies in \textbf{C++} and \textbf{ Java}.
\end{tightemize}
\sectionsep

    \resumeHeading{BlueJay}{QA Engineer Intern}{Remote}{Dec 2018 - Mar 2019}
\begin{tightemize}
    \item Verified production tier supply chain integration software.
    \item Created, implemented, and validated test case scenarios for production code and software. 
\end{tightemize}
\sectionsep

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Swap degree and school if your school is reputable
\educationHeading{University of Washington}{Geographic Information Systems}{Seattle, WA}{June 2020}


% \courseWork{Data Structures and Algorithms; Operating Systems;  Computer Security; Software Testing; Advanced Networking; Big Data Analytics}
\sectionsep
%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}
\Project{DoD Backend Service}{}
\descript {Javascript, AWS, APIs, Postman}\\
Implemented a backend search service for Jonathan Little's "Deck of Degeneracy" that allows authorized users to search for owners of specific card hands (1-d = Ace of Diamonds, 13-s = King of Spades). Utilized the Moralis Web3 API to fetch collection holder data, Firebase to store card ownership data in intervals of 15 minutes, and AWS EC2 to host the backend source code.

\Project{NFT Collection Generator}{}
\descript {Java, Javascript, JSON}\\
Contracted to design \& implement multiple production tier NFT collection generators that take a set of weighted art files/assets and layer them on each other to create randomly generated art collections (Metapengus, BobbleBats, Sneaks of Nature, Deck of Degeneracy). Wrote a JSON parser in Java that edits all JSON files in a folder to include IPFS URIs of NFTs.
\sectionsep

\Project{Relic Punks}{}
\descript{NFTs, Solidity, DevOps}\\
Contracted by Ikonick (founded by artist Jeff Cole) to build the Metarelics.xyz website \& implement a custom smart contract. Implemented structs and dynamic metadata generating functions for each token, and utilized a Merkle Proof (tree hash) to verify user purchase eligibility. 
\sectionsep

\Project{Memory Manager}{}
\descript{C, Valgrind, GDB, Gitlab}\\
A program that mimics the C standard library's malloc and free by implementing a LinkedList of memory blocks sorted by size.
\sectionsep

\Project{Fear Filter}{}
\descript{ JavaScript, Java, HTML \& CSS}\\
A Chrome extension that allows users to use keywords to filter out undesired images (from phobias to movie/TV spoilers). Created at the Dubhacks Hackathon.
\sectionsep

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------

\section{Skills}
\begin{resumeSkillList}
    \singleItem{Languages:}{Java, Solidity, C++, Python, C}
    \\
    \singleItem{Web Development:}{React, JavaScript, HTML/CSS, NodeJS}
    \\
    \singleItem{Technologies:}{Git, Kubernetes, Unix, Firebase, Postman, Moralis, ImmutableX, AWS: Amplify, EC2, S3}
\end{resumeSkillList}
\sectionsep
\end{document}

